---
title: "Plug-in JVS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plug_in_JVS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(JDCruncheR)
library(rjwsacruncher)
```

## Introduction

This vignette explains how to create a JVS Quality Report with the rjd3qr package. This only works for v3.

## Creation of demetra_m.csv

To create a JVS Quality Report, you need to use the Cruncher with specific options, using the rjwsacruncher package. If you do not have downloaded the JDemetra+ Cruncher, you can download it from github : https://github.com/jdemetra/jdplus-main/releases. The file you should download starts with "jwsacruncher-standalone". 

The goal of this step is to generate a demetra_m file containing a lot of informations on series to study, and also several files containing the components of the series.

To generate those files, you need to use the Cruncher with the following options:

```{r, echo=TRUE, eval=FALSE}
options(
    is_cruncher_v3 = TRUE,
    default_matrix_item = c(
        "span.start",
        "span.end",
        "log",
        "span.n",
        "regression.nout",
        "regression.ntd",
        "m-statistics.m7",
        "decomposition.seasonal-filters",
        "decomposition.trend-filter",
        "decomposition.d7-trend-filter",
        "quality.summary",
        "regression.lp",
        "regression.leaster",
        "diagnostics.seas-sa-ac1:3",
        "diagnostics.seas-sa-ac1",
        "diagnostics.seas-lin-combined",
        "regression.out(*)",
        "regression.td-ftest:3",
        "residuals.lb:3",
        "diagnostics.td-sa-last:2",
        "diagnostics.seas-sa-f:2",
        "arima.p", "arima.d", "arima.q", "arima.bp", "arima.bd", "arima.bq",
        "m-statistics.q", "m-statistics.q-m2"
     ),
    default_tsmatrix_series = c(
        "decomposition.y_cmp",
        "decomposition.s_cmp",
        "decomposition.sa_cmp", 
        "decomposition.t_cmp"
    )
)

rjwsacruncher::cruncher_and_param(
    workspace = "path/to/the/workspace/file.xml",
    cruncher_bin_directory = "path/to/the/cruncher/v3/bin_directory",
    csv_layout = 'vtable',
    short_column_headers = FALSE,
    refreshall = FALSE,
    v3 = TRUE,
    delete_existing_file = TRUE,
    policy = "None"
)

```

At this step, you should have generated 5 files.

## Creation of report JVS

Once the Cruncher has generated the right outputs, the JVS Quality Report can be generated.

```{r, echo=TRUE, eval=TRUE}
# Path leading to the directory containing the needed files:
dir_path <- system.file(
"extdata",
"WS/WS_world/Output/SAProcessing-1",
package = "JDCruncheR"
)

JVS <- extract_JVS(dir = dir_path)
```

The JVS object is a dataframe containing the quality report. To save it, you need to export it.

## Export

To export the JVS Quality Report, you need to use the writing function. The report can be exported as a csv file:

```{r, echo=TRUE, eval=FALSE}
write(JVS, format = "csv", export_dir = "path/to/the/export/directory", overwrite = TRUE)
```


The report can be exported as a xlsx file:

```{r, echo=TRUE, eval=FALSE}
write(JVS, format = "xlsx", export_dir = "path/to/the/export/directory", overwrite = TRUE)
```
